\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-27 analytics/npa.tex
Minor edits

\subsection{Direct search (requirement criteria)}

@@

  The difference between these results and those in \ref{fig:navs-combined} is suble but logical. Users searching for a specific course should have an increased proportion of 1-navigation adds, as the graph shows, because the use-case is \emph{search for course}, \emph{add course}, perhaps occasionally taking an extra try to account for typos, not knowing the title or course code exactly, etc.

  But given this reasoning, why would 0-navigation adds still be so common in direct searches? Further analysis on only the sections that were added from direct search and with 0 navigations shows that 64\% of those sections are in fact \emph{subsections}. As happened in the illustrative example at the beginning of this section, this shows that a very common use-case is to add labs, workshops, etc. of a course directly after adding the main section.

  This hypothesis is further confirmed by doing the same analysis for ${navs}=1$ and ${navs}=2$, when the inverse behavior would be expected (it makes sense for subsections which were added seperately from their main sections to be more rate). Only 11\% of sections that were added from a direct search after 1 navigation are subsections, and that number drops to 8\% for 2 navigations.

\subsection{Browse (elective criteria)}

@@

\subsection{Peer-guided (recommendation criteria)}

>>>>

\subsection{Direct search (required courses)}

@@

  The difference between these results and those in Figure \ref{fig:navs-combined} is subtle but logical. Users searching for a specific course should have an increased proportion of 1-navigation adds, as the graph shows, because the use-case is ``\emph{search for course}'' followed by ``\emph{add course}'', perhaps occasionally taking an extra try to account for typos, etc.

  But given this reasoning, why would 0-navigation adds still be so common in direct searches? Further analysis on sections added from 0 navigations (from direct search) shows that 64\% of those sections were in fact \emph{subsections}. As was illustrated in the example at the beginning of this section, this demonstrates the very common use-case of adding labs, workshops, etc. of a course directly after adding the main section when directly searching.

  This hypothesis is further confirmed by doing the same analysis for ${navs}=1$ and ${navs}=2$, when the inverse behavior would be expected (it makes sense for subsections which were added seperately from their main sections to be more rare). Only 11\% of sections that were added from a direct search after 1 navigation were subsections, and that number drops to 8\% for 2 navigations.

\subsection{Browse (elective courses)}

@@

\subsection{Peer-guided (recommended courses)}

### 2016-04-27 design/search.tex
Minor edits

I have identified \emph{three} use-cases for course searching (the existence of and distinction between these cases will be demonstrated with collected usage data in Chapter 4). The types of courses user look for are \textbf{requirements}, \textbf{electives}, and \textbf{peer recommendations} (associated with direct, exploratory, and peer-guided search, respectively). SkedgeQL and other application features offer substantial improvements over CDCS for each of these cases.

>>>>

I have identified \emph{three} use-cases for course searching (the existence of and distinction between these cases will be demonstrated with collected usage data in Chapter 4). The types of courses users look for are \textbf{requirements}, \textbf{electives}, and \textbf{peer recommendations} (associated with direct, exploratory, and peer-guided search, respectively). SkedgeQL and other application features offer substantial improvements over CDCS for each of these cases.

### 2016-04-27 design/social.tex
Minor edits

  \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social-login}
      }
      \caption[Skedge Social landing page for a user who hasn't yet joined it]{Skedge Social landing page (\url{http://skedgeur.com/social}) for a user who hasn't yet joined it. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible with the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

@@

  This has the advantage of organizing and persisting peers' schedules, solving the first three issues of the ``Facebook post'' model listed above.

@@

  Skedge Social also integrates into course search results, showing the user any other peers on the platform who are taking, have taken, or \emph{liked} courses in the results list (see Figure \ref{fig:sk-social-course}). This has several advantages, which solve the last ``Facebook post'' model issue listed above:

>>>>

  \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social-login}
      }
      \caption[Skedge Social landing page for a user who hasn't yet joined it]{Skedge Social landing page (\url{http://skedgeur.com/social}) for a user who hasn't yet joined it. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible from the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

@@

  This has the advantage of organizing and persisting peers' schedules, solving the first two issues of the ``Facebook post'' model listed above.

@@

  Skedge Social also integrates into course search results, showing the user any other peers on the platform who are taking, have taken, or \emph{liked} courses in the results list (see Figure \ref{fig:sk-social-course}). This has several advantages, which solve the last two ``Facebook post model'' issues listed above:
